Git Learning Notes

### 2014-02-16 foo.tex
finish lynda tutorial on git

% remotes 
git push -u %

>>>>

% remotes 
git push -u % -u = --set-upstream
git branch -r % show remote branch
git branch -a % show all branches

fetch % synch origin/master with remote 
fetch does not merge origin/master into local master branch

git pull = git fetch + git merge

git branch no_track origin/nontrakcing % starting a new branch from origin/nontracking

git show HEAD
git show branch

git log -p onebranch..another
